\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-02-07 tex/figuressupp.tex
recombine figures
revise
update main text
minor edits
redistribute text between main text and supplement
'Merge' figuressupp from 'science' branch

@@

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.7\columnwidth]{fig/region2and3.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two and three component systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial.}
% \label{fig:region2and3}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.5\columnwidth]{fig/region2x2.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two component systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial. Colors correspond to the regions given in the main text Green: $R_{2000}$, Red: $R_{1100}$, Yellow: $R_{0200}$, Magenta: $R_{0002}$, Blue: $R_{0020}$.}
% \label{fig:region2x2}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.5\columnwidth]{fig/region3x3.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for three component systems.} Colors correspond to the following regions Green: $R_{3000}$, Red: $R_{1200}$, Yellow: $R_{1002}$, Blue: $R_{1020}$. This is the plane $s_3=1$.}
% \label{fig:region3x3}
% \end{figure}

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.9\columnwidth]{fig/jacobianvectorfields.pdf}
\caption{{\bf Vector fields resulting from the random sampling of two component systems.} System parameters of \ref{eq:arbitraryjacobianreactionnetwork} are rescaled to ensure the fixed point is located at $(1,1)$. The color of the dot located at the fixed point indicates whether it is stable (black) or unstable (gray).}
\label{fig:jacobianvectorfields}
\end{figure}

\pagebreak

@@

\pagebreak

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/apstab3x3.pdf}
\caption{{\bf System stability as a function of connectivity.} The red points represent the average of system stability at each connectivity.}
\label{fig:apstab3x3}
\end{figure}

\pagebreak
\FloatBarrier

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/cycle3x3.pdf}
\caption{{\bf dynamical robustness as a function of number of cycles.} }
\label{fig:cycle3x3}
\end{figure}

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.7\columnwidth]{fig/region2and3.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two and three variable systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial.}
% \label{fig:region2and3}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.5\columnwidth]{fig/region2x2.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two variable systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial. Colors correspond to the regions given in the main text Green: $R_{2000}$, Red: $R_{1100}$, Yellow: $R_{0200}$, Magenta: $R_{0002}$, Blue: $R_{0020}$.}
% \label{fig:region2x2}
% \end{figure}

@@

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.5\columnwidth]{fig/region3x3.pdf}
% \caption{{\bf Stability conditions on coefficients of the characteristic polynomial for three variable systems.} Colors correspond to the following regions Green: $R_{3000}$, Red: $R_{1200}$, Yellow: $R_{1002}$, Blue: $R_{1020}$. This is the plane $s_3=1$.}
% \label{fig:region3x3}
% \end{figure}
